%
\documentclass[10pt]{article}

% The usual packages
\usepackage{fullpage}
\usepackage{breakcites}
\usepackage{setspace}
\usepackage{endnotes}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{rotating}
\usepackage{dcolumn}
\usepackage{longtable}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{hyperref}
%\usepackage[usenames,dvipsnames]{color}
\usepackage{url}
\usepackage{natbib}
\usepackage{framed}
\usepackage{epigraph}
\usepackage{lipsum}
\usepackage{subcaption}
\usepackage{parskip}
\usepackage{hanging}
\usepackage[left]{lineno}

\usepackage[font=small,labelfont=sc]{caption}
%\restylefloat{table}
\bibpunct{(}{)}{;}{a}{}{,}

% place figures at the end
\usepackage{endfloat}
\renewcommand{\listoffigures}{} % but suppress these lists
\renewcommand{\listoftables}{} % suppress these lists

% Set paragraph spacing the way I like
\parskip=0pt
\parindent=20pt

% Define mathematical results
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{claim}{Claim}
\newenvironment{proof}[1][Proof]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{definition}[1][Definition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{example}[1][Example]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{remark}[1][Remark]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

% Set up fonts the way I like
%\usepackage{tgpagella}
%\usepackage[T1]{fontenc}
%\usepackage[bitstream-charter]{mathdesign}

%% Set up lists the way I like
% Redefine the first level
\renewcommand{\theenumi}{\arabic{enumi}.}
\renewcommand{\labelenumi}{\theenumi}
% Redefine the second level
\renewcommand{\theenumii}{\alph{enumii}.}
\renewcommand{\labelenumii}{\theenumii}
% Redefine the third level
\renewcommand{\theenumiii}{\roman{enumiii}.}
\renewcommand{\labelenumiii}{\theenumiii}
% Redefine the fourth level
\renewcommand{\theenumiv}{\Alph{enumiv}.}
\renewcommand{\labelenumiv}{\theenumiv}
% Eliminate spacing around lists
\usepackage{enumitem}
\setlist{nolistsep}

% Create footnote command so that my name
% has an asterisk rather than a one.
\long\def\symbolfootnote[#1]#2{\begingroup%
\def\thefootnote{\fnsymbol{footnote}}\footnote[#1]{#2}\endgroup}

% Create the colors I want
\usepackage{color}
\definecolor{darkred}{RGB}{100,0,0}

\hypersetup{
pdftitle={Unreliable Inferences about Unobserved Processes}, % title
pdfauthor={Carlisle Rainey and Robert A. Jackson}, % author
pdfkeywords={partial observability} {split population}
pdfnewwindow=true, % links in new window
colorlinks=true, % false: boxed links; true: colored links
linkcolor=black, % color of internal links
citecolor=black, % color of links to bibliography
filecolor=black, % color of file links
urlcolor=blue % color of external links
}

% enable comments in pdf
\newcommand{\kelly}[1]{\textcolor{darkred}{#1}}
\newcommand{\carlisle}[1]{\textcolor{magenta}{#1}}

% April 6 Statistics Politics Policy submission
\begin{document}
%\linenumbers
\begin{center}
{\LARGE \textbf{Appendix}}\\\vspace{4mm}

{\large \textbf{Unreliable Inferences about Unobserved Processes}}

\vspace{10mm}

Carlisle Rainey\symbolfootnote[2]{Carlisle Rainey is Assistant Professor of Political Science, Texas A\&M University, 2010 Allen Building, College Station, TX, 77843 (\href{mailto:crainey@tamu.edu}{crainey@tamu.edu}).}

\vspace{3mm}

Robert A. Jackson\symbolfootnote[3]{Robert A. Jackson is Professor of Political Science, Florida State University, 531 Bellamy Building, Florida State University, Tallahassee, FL 32306 (\href{mailto:rjackson@fsu.edu}{rjackson@fsu.edu}).}
\end{center}

\vspace{10mm}

\section{Algorithm for Wrong Link Function Simulations}\label{app:link}

\begin{enumerate}
\item Choose $n_x$ and $n_z$ independently from a Poisson distribution with mean 1.5. If both $n_x$ and $n_z$ equal zero, then set $n_z$ equal to one.
\item Choose $n_w - 1$ from a Poisson distribution with mean 0.5.
\item Assign a type (continuous or binary) to each of the $n_x + n_z + n_w$ variables with equal probability. To simplify the computation, continuous variables take on the values 0.0, 0.2, 0.4, 0.6, 0.8, or 1.0, and binary variables take on the values 0 or 1.
\item To simplify the computation, create a data set $WXZ$ that contains each possible combination of all of the explanatory variables.
\item Choose the preliminary coefficients $\beta^*$ and $\gamma*$ from a normal distribution. The intercept coefficients come from a normal distribution with mean 0 and standard deviation 2. The slope coefficients come from a normal distribution with mean 0 and standard deviation 1.
\item If the link function of the DGP is logit, then set $\beta$ equal to $\beta^*$ and $\gamma$ equal to $\gamma^*$. If the link function is some other function $g$, then (1) simulate a large data set from the logit DGP, (2) estimate a model with link function $g$ to that data set, and (3) set $\beta$ and $\gamma$ equal to the estimates $\hat{\beta}$ and $\hat{\gamma}$, respectively. This step scales the coefficients so that the quantities of interest have comparable magnitude regardless of the DGP.
\item Using the parameters $\beta$ and $\gamma$, simulate 100,000,000 values of $y_{obs}$ and $d_{main}$ for each combination of the explanatory variables.
\item Fit a full observability model to the outcome variable $d_{main}$. Calculate the first difference as $w_1$ moves from 0 to 1. Store this large-sample estimate.
\item Fit a partial observability model to the observed outcome variable $y_{obs}$. Calculate the first difference as $w_1$ moves from 0 to 1. Store this large-sample estimate.
\end{enumerate}

\section{Algorithm for Monotonic Link Function Simulations}\label{app:mon}

\begin{enumerate}
\item Choose the coefficients for the non-linear, interactive equations.
\begin{equation}
\Pr(d_{main}) = \beta_{cons} + \beta_w w + \beta_{w^2} w^2 \nonumber
\end{equation}
and 
\begin{equation}
\Pr(d_{nuisance}) = \gamma_{cons} + \gamma_w w + + \gamma_z z + \gamma_{w^2} w^2 + \gamma_{z^2} z^2 + \gamma_{wz} wz \text{.}\nonumber
\end{equation}
from a uniform distribution that ranges from -1 to 1.
\item Check that this link function produces a monotonic relationship between the $w$ and $\Pr(d_{main})$ and between $w$ and $z$ $\Pr(d_{nuisance})$. 
\item Set $w$ as either binary or continuous. For computational ease, continuous variables take on the values 0.0, 0.2, 0.4, 0.6, 0.8, or 1.0, and binary variables take on the values 0 or 1.
\item Create a data set $WZ$ that contains each possible combination of $w$ and $z$. 
\item For each row in $WZ$, simulate 100,000,000 values of $y_{obs}$ and $d_{main}$.
\item Fit a full observability model to the outcome variable $d_{main}$. Calculate the first difference as $w_1$ moves from 0 to 1. Store this large-sample estimate.
\item Fit a partial observability model to the outcome variable $y_{obs}$. Calculate the first difference as $w_1$ moves from 0 to 1. Store this large-sample estimate.
\end{enumerate}

\end{document}